Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-26 snapshot_system/fast14_evaluation.tex
revise

Figure~\ref{fig:exbin-efficiency-graph2} also shows the curve  of VC without local similarity search.
Adding local similarity-guided search increases deduplication efficiency from 93\% to over 96\%.
That is one significant improvement compared to the work in ~\cite{WeiZhangIEEEClound}.
The reason is that  
%Without this (i.e. when we only check the parent segment at the same offset), 
when a data  segment is moved to another location on disk, for example when a file is rewritten
rather than modified in place,  dirty-bit based detection would not be able to detect such a movement.
 We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently,
so the similarity search becomes important for those VMs.
% In general, our experiments show that
% dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
% which leads about a 75.86\% reduction.
% Similarity-guided local search can further reduce the data size
% to about 12.05\% of original size, namely it delivers an additional 12.09\% reduction.
% The PDS-based global duplicate detection with $\sigma=2\% $
% can reduce the size further to 8.6\% of original size, namely it 
% delivers an additional 3.45\% reduction.
In general, our experiments show that
dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
which leads to about a 75.86\% reduction.
Similarity-guided local search can further reduce the data size
to about 12.05\% of original, namely it delivers a 50.08\% reduction to the dirty segments.
The popularity-guided global deduplication with $\sigma=2\% $
can reduce the data further to 8.6\% of its original size, so
it provides additional 28.63\% reduction to the remaining data.

@@

% \begin{table*}[t]
%     \centering
%     \begin{tabular}{c|ccc|ccc}
%     Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    & \multicolumn{3}{c}{Throughput with} \\
%     backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-7}
%     per node                & Raw                                        & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\ \hline
%     1                       & 1369.6                                     & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
%     2                       & 2408.5                                     & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
%     4                       & 4101.8                                     & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
%     6                       & 5456.5                                     & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
%     \end{tabular}
% \caption{Throughput of software layers under different concurrency}
% \label{tab:throughput}
% \end{table*}
\begin{table}[htbp]
    \centering
    \begin{tabular}{c|ccc}
    Num. of concurrent      & \multicolumn{3}{c}{Throughput without}    \\
    backup tasks            & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-4}
    per node                & Backup                                     & Snapshot Store & QFS  \\ \hline
    1                       & 1369.6                                     & 148.0          & 35.3 \\
    2                       & 2408.5                                     & 260.2          & 61.7 \\
    4                       & 4101.8                                     & 443.3          & 103.1 \\
    6                       & 5456.5                                     & 589.7          & 143.8 \\
    \end{tabular}
\caption{Throughput of software layers per machine under different concurrency}
\label{tab:throughput}
\end{table}

>>>>

Figure~\ref{fig:exbin-efficiency-graph2} also shows the curve  of VC without local similarity search.
Adding local similarity-guided search increases deduplication efficiency from 93\% to over 96\%.
That is one significant improvement compared to the work in ~\cite{WeiZhangIEEEClound}
which uses the parent segment at the same offset to detect duplicates locally.
The reason is that  
%Without this (i.e. when we only 
when a data  segment is moved to another location on disk, for example when a file is rewritten
rather than modified in place,  dirty-bit based detection would not be able to detect such a movement.
 We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently,
so the similarity search becomes important for those VMs.
% In general, our experiments show that
% dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
% which leads about a 75.86\% reduction.
% Similarity-guided local search can further reduce the data size
% to about 12.05\% of original size, namely it delivers an additional 12.09\% reduction.
% The PDS-based global duplicate detection with $\sigma=2\% $
% can reduce the size further to 8.6\% of original size, namely it 
% delivers an additional 3.45\% reduction.
In general, our experiments show that
dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
which leads to about a 75.86\% reduction.
Similarity-guided local search can further reduce the data size
to about 12.05\% of original, namely it delivers a 50.08\% reduction to the dirty segments.
The popularity-guided global deduplication with $\sigma=2\% $
can reduce the data further to 8.6\% of its original size, so
it provides additional 28.63\% reduction to the remaining data.

@@

% \begin{table*}[t]
%     \centering
%     \begin{tabular}{c|ccc|ccc}
%     Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    & \multicolumn{3}{c}{Throughput with} \\
%     backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-7}
%     per node                & Raw                                        & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\ \hline
%     1                       & 1369.6                                     & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
%     2                       & 2408.5                                     & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
%     4                       & 4101.8                                     & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
%     6                       & 5456.5                                     & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
%     \end{tabular}
% \caption{Throughput of software layers under different concurrency}
% \label{tab:throughput}
% \end{table*}
\begin{table}[htbp]
\begin{small}
    \centering
    \begin{tabular}{c|ccc}
    Num. of concurrent      & \multicolumn{3}{c}{Throughput without}    \\
    backup tasks            & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-4}
    per machine                & Backup                                     & Snapshot Store & QFS  \\ \hline
    1                       & 1369.6                                     & 148.0          & 35.3 \\
    2                       & 2408.5                                     & 260.2          & 61.7 \\
    4                       & 4101.8                                     & 443.3          & 103.1 \\
    6                       & 5456.5                                     & 589.7          & 143.8 \\
    \end{tabular}
\end{small}
\caption{Throughput of software layers per machine under different concurrency}
\label{tab:throughput}
\end{table}
